Prefetching SPARQL query cacher

### 2016-05-16 dissertation/cache-proxy.tex
finish the desc of Attean
start description of caching proxy

That new plan types can be integrated into the planner with ease, and
that the  planner itself can be changed with very little effort is a
key contribution of the Attean system, which I have taken advantage of
in this work. That this is made easy is to the credit of traits, as

@@

\subsection{The query proxy}\label{sec:cacher}

>>>>

That new plan types can be integrated into the planner with ease, and
that the planner itself can be changed with very little effort is a
key contribution of the Attean system, which I have taken advantage of
in this work. That this is made easy is to the credit of traits, as
will become clear as we study the details of the implementation in
Section~\ref{sec:cacher}.

@@

\subsection{The caching proxy}\label{sec:cacher}

The caching proxy consists of several components:

\begin{itemize}
\item An analyser, used to determine whether certain triple patterns
  should have their results prefetched and cached.
\item A prefetcher that performs the needed actions.
\item Two query planners, one that can use a local cache and a remote
  endpoint, and another that extends this to be able to use Triple
  Pattern Fragments as well, and corresponding models.
\item Two roles to generate plans for accessing cache and Triple
  Pattern Fragments and a corresponding plan class to enter results
  in the cache.
\item A custom User Agent for caching.
\item The actual caching proxy that accepts queries, runs the planner
  and returns the results.
\item Scripts to run the whole system.
\end{itemize}
